### 2012-09-04 sections/design.tex
* penultimate PDF
penultimate, corrections
the listings don't break into multiple pages

The grouper performs aggregation of the input flow-records data. It consists
of a number of terms that correspond to a specific clause. A flow-record in
order to be a part of the group should satisfy at-least one clause. A
flow-record, although, can be a part of multiple clauses, it cannot be part of
multiple groups. The grouping terms can be either absolute or relative. The
newly formed groups, which are passed on to the group filter, can also contain
meta-information about the flow-records contained within the group using the
aggregate clause defined as part of the grouper query.

@@

The merger performs relative filtering on the N-tuples of groups formed from
the N stream of groups passed on from the group-filter as input. The relative
filtering on the groups are applied to express timing and concurrency
constraints using Allen interval algebra \cite{fallen:1983}. The ungrouper is
the final processing element of the pipeline. It unwraps the tuples of
group-records into individual flow-records, ordered by their timestamps. Any
duplicate flow-records appearing from several group-records are eliminated and
are sent as output only once.

>>>>

The grouper performs aggregation of the input flow-records. A flow-record in
order to be a part of the group should satisfy at-least one clause. A
flow-record, although, can be a part of multiple clauses, it cannot be part of
multiple groups. The grouping terms can be either absolute or relative. The
newly formed groups, which are passed on to the group filter, can also contain
meta-information about the flow-records contained within the group using the
aggregate clause defined as part of the grouper query. The possible
aggregation operations are \emph{static, count, product, sum, logical
and/or/xor, arithmetic mean, standard deviation, union, median, minimum and
maximum}.

@@

The merger performs relative filtering on the N-tuples of groups formed from
the N stream of groups passed on from the group-filter as input. The relative
filtering on the groups are applied to express timing and concurrency
constraints using Allen interval algebra \cite{fallen:1983}.

The ungrouper is the final processing element of the pipeline. It unwraps the
tuples of group-records into individual flow-records, ordered by their
timestamps. Any duplicate flow-records appearing from several group-records
are eliminated and are sent as output only once.
